%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Daniel Velasco} \\ \vspace{1pt}
    \small +57 320-916-8731 $|$ \href{mailto:dvelascogz@gmail.com}{\underline{dvelascogz@gmail.com}} $|$ \href{https://daniel-velasco.vercel.app/}{\underline{daniel-velasco.vercel.app}}
\end{center}

%-----------SUMMARY-------------
\small AI Systems and Full-Stack Developer with production experience building RAG pipelines, AI agents, and SaaS platforms. Specialized in FastAPI, React, TypeScript, and LangGraph. Delivered end-to-end systems---from architecture design to cloud deployment---across startups and applied research environments.

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sergio Arboleda University}{Bogotá DC, Colombia}
      {Computer Science and Artificial Intelligence Engineering}{Feb. 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Honors Program ``Rodrigo Noguera Laborde'' -- First and Second Distinction.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer \& AI Tools Developer}{March 2025 -- Present}
      {Dantalabs}{Bogotá, Colombia}
      \resumeItemListStart
        \resumeItem{Built production full-stack applications using FastAPI, React, TypeScript, Docker, and PostgreSQL.}
        \resumeItem{Developed AI agents and multi-step workflows using LangGraph; designed scalable backend APIs.}
        \resumeItem{Implemented MCP servers and integrated AI tools with Microsoft Copilot; deployed and monitored services in production.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer \& Data Architect}{December 2024 -- December 2025}
      {SAM | Automated Meteorological Services}{Bogotá, Colombia}
      \resumeItemListStart
        \resumeItem{Architected a climate forecasting platform for solar energy systems using Python, Pandas, and Open-Meteo APIs.}
        \resumeItem{Built React dashboards with real-time metrics; deployed Django REST backend on AWS (EC2, RDS, S3, Lambda).}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Developer}{August 2023 -- December 2024}
      {Dataexco}{Duitama, Colombia}
      \resumeItemListStart
        \resumeItem{Led migration of a legacy academic system to a modern web platform using Django and MySQL.}
        \resumeItem{Delivered frontend interfaces and internal tooling that improved academic and administrative workflows.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{OrbitEngine} $|$ \emph{FastAPI, React, TypeScript, PostgreSQL, Railway} $|$ \href{https://orbitengine.lat}{\underline{orbitengine.lat}}}{Nov. 2025 -- Apr. 2026}
          \resumeItemListStart
            \resumeItem{Built and deployed a multi-tenant SaaS platform centralizing inventory, client, and sales operations for SMEs.}
            \resumeItem{Implemented real-time low-stock alerts and daily sales analytics dashboards; owned full development lifecycle from design to production maintenance.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Coastal Jurisprudence AI Agent} $|$ \emph{RAG, LangGraph, FastAPI, Next.js, Chroma, Ollama, Firebase}}{Mar. 2026 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a production RAG system for Colombian coastal jurisprudence, used by lawyers for AI-assisted case research.}
            \resumeItem{Built a PDF ingestion pipeline with Docling, Chroma vector DB, and Ollama embeddings; integrated Firebase for auth and chat persistence.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Co-Founder \& CTO} $|$ \emph{Tech Craft Solutions}}{June 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Founded a software company delivering custom AI-driven and full-stack solutions; defined architectures and led end-to-end development.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, TypeScript, JavaScript, SQL, Java, C\#, HTML/CSS, Golang} \\
     \textbf{Frontend}{: React, Next.js, TailwindCSS, TanStack, ShadCN} \\
     \textbf{Backend}{: FastAPI, Django, Flask, .NET, Node.js} \\
     \textbf{AI \& Data}{: LangGraph, RAG systems, MCP, Chroma, Ollama, Pandas, NumPy} \\
     \textbf{Cloud \& DevOps}{: Docker, AWS (EC2/RDS/S3/Lambda), Railway, Google Cloud Platform} \\
     \textbf{Databases}{: PostgreSQL, MySQL, MongoDB, Firebase, Oracle SQL}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
